Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'

### 2023-03-21 supplements/supplements.Rmd
set up repo

---
title             : "Variation in gaze understanding across the life span: A process-level perspective"
shorttitle        : "modeling variation in gaze understanding"
author:

@@

  - name          : "Manuel Bohn"
    affiliation   : "1"
  - name          : "Luke Maurits"
    affiliation   : "1"
  - name          : "Annika Werwach"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Abstract

keywords          : "social cognition, individual differences, gaze cues, cognitive modeling"
wordcount         : "xxx"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include = FALSE}
library("papaja")
library("ggplot2")
library("ggpubr")
library("tidyverse")
library("brms")
theme_set(theme_classic())
```

@@

```{r load_data}
# testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
#   # determine order of factors
#   mutate(
#     targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
#     studyversion = factor(studyversion, levels = c("hedge", "box")), 
#     datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
#     sample = factor(sample, levels = c("kids", "adults")), 
#     studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
#   )
```

# Introduction
- why do we care about developmental trajectory? ref to stat learning paper
- variation

# Lifespan 
- development & individual differences in gaze understanding
- verweis methods paper reliable differences kinder & adults. 
- kontinuerliche, systematische variation, wodrin? => model

# Computational cognitive model
- model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
- entwicklungsperspektive basierend auf model
- dann prozess-ebene => magnet

# Non-social vector following

## Analysis
All test trials without voice-over descriptions were included in our analyses.
We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].

```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
# knitr::include_graphics("../figures/screenshot.png")
```

# Declarations

## Open practices statement

The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
The data sets generated during and/or analysed during the current study are available in the [gazecues-modeling] repository (<https://github.com/ccp-eva/gazecues-modeling>).
All experiments were pre-registered (<https://osf.io/zjhsc/>).

## Funding

This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
We thank all the children, caregivers, and adults who participated in the study.
We thank Jana Jurkat for her help with data collection.

## Conflicts of interest

The authors declare that they have no conflict of interest.

## Consent to participate

Informed consent was obtained from all individual participants included in the study or their legal guardians.

## Authors' contributions

The authors made the following contributions:
### TODO

>>>>

---
title             : "Supplements for the manuscript  'Variation in gaze understanding across the life span: A process-level perspective'"
shorttitle        : "Supplements"
author:

@@

  - name          : "Manuel Bohn"
    affiliation   : "1"
  - name          : "Luke Maurits"
    affiliation   : "1"
  - name          : "Annika Werwach"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
library("ggpubr")
library("kableExtra")
theme_set(theme_classic())
```

@@
